% !TeX encoding = UTF-8
% !TeX spellcheck = en_GB

%%% Add [final] option to the report class to switch between draft and final version of the report
%%% Use [narrowmargin] to enable narrow margins - this may impair readability.
%\documentclass[a4paper,12pt,draft]{include/intocpsreport}   %Or
\documentclass[a4paper,12pt,final]{include/intocpsassociation}   %Or
% intocpslargereport if chapters are required.
%
%
%
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{tikz-uml}
\usepackage{framed}
\usepackage{subcaption}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{color}
\usepackage{amsmath}
\usepackage{courier}
\usepackage{xspace}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{textcomp} % Used for 20-sim section \textrightarrow
%\usepackage{showframe}

\usepackage{listings}
\input{listings-modelica.cfg}

% The VDMlisting package loads the times package which changes the font so we just mark it as loaded to prevent the load. 
\makeatletter
\@namedef{ver@times.sty}{}% a fake for a "loaded" package
\makeatother
\usepackage{vdmlisting}

%% Define listing environment for XML
\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}

\lstset{
  basicstyle=\footnotesize\ttfamily,
  columns=fullflexible,
  showstringspaces=false,
  commentstyle=\color{gray}\upshape
}

\lstdefinelanguage{XML}
{
  morestring=[b]",
  morestring=[s]{>}{<},
  morecomment=[s]{<?}{?>},
  stringstyle=\color{black},
  identifierstyle=\color{darkblue},
  keywordstyle=\color{cyan},
  morekeywords={xmlns,version,type}% list your attributes here
}


\lstnewenvironment{xml}[1][]{\lstset{  language=XML,
  morekeywords={encoding, xs:schema,xs:element,xs:complexType,xs:sequence,xs:attribute}}\lstset{#1}}
{}

%% end listing environment for XML
%
%
%
\def\draftnote#1{\noindent\smallskip\framebox{\begin{minipage}{0.95\columnwidth}\color{red}#1\end{minipage}}\smallskip\par}
\newenvironment{draftnoteenv}{\noindent\smallskip\begin{framed}\begin{minipage}{0.95\columnwidth}\color{red}}{\end{minipage}\end{framed}\smallskip\par}
\newenvironment{assumption}{\noindent\smallskip\color{blue}\begin{framed}\begin{minipage}{0.95\columnwidth}}{\end{minipage}\end{framed}\smallskip\par}
%
%
%
\newcommand{\revisit}[1]{\textcolor{red}{\pmb{[[[}\@ #1\@ \pmb{]]]}}}
\newcommand{\intoapp}{INTO-CPS Application}
\newcommand{\into}{INTO-CPS\xspace}
%
%
%\reportnumber{D4.3a}
\reporttitle{INTO-CPS Tool Chain User Manual}
%\reporttitle{User Manual for the INTO-CPS Tool Chain}
\shortreporttitle{INTO-CPS Tool Chain User Manual}  %To use if report title is too long for header
%
%
%
%%% Set document release class as appropriate
%%% e.g. Public, Restricted, Programme Participant
\reportstatus{Public}
%
%
%
%%% If document is a deliverable, this flag should be commented out 
%%% e.g. %\technotetrue
%%% If report is a technical report, leave uncommented
%%% e.g. \technotetrue
%\technotetrue % Comment out as appropriate
%
%
%
\submissiondate{September, 2018}
\contributors{
Victor Bandur, AU\\
Peter Gorm Larsen, AU\\ 
Kenneth Lausdahl, AU \\
Casper Thule, AU\\
Carl Gamble, UNEW\\
Richard Payne, UNEW\\
Adrian Pop, LIU\\
Etienne Brosse, ST\\
J{\"o}rg Brauer, VSI\\
Florian Lapschies, VSI\\
Marcel Groothuis, CLP\\
Tom Bokhove, CLP\\
Christian Kleijn, CLP\\
Luis Diogo Couto, UTRC\\
Christian K\"{o}nig, TWT
}
%
%
%
\editors{
  Peter Gorm Larsen, AU
}
%
%
%
%\reviewers{Ken Pierce, UNEW\\
%Kangfeng Ye, UY\\
%Luis Diogo Couto, UTRC}
%
%
%
%% Version details  
% #1: version
% #2: date
% #3: author
% #4: description
\addversion{0.01}{11-01-2017}{Victor Bandur}{Initial version.}
\addversion{0.02}{30-10-2017}{Victor Bandur}{Updates for internal review.}
\addversion{0.03}{30-10-2017}{Marcel Groothuis}{Added 20-sim 4C FMI import/export manual.}
\addversion{0.04}{12-12-2017}{Marcel Groothuis}{Address internal review comments 20-sim and 20-sim 4C sections.}
\addversion{1.0}{18-12-2017}{Victor Bandur}{Final version inside the INTO-CPS project.}
\addversion{1.1}{26-02-2018}{Peter Gorm Larsen}{First version in the INTO-CPS association.}
\addversion{1.2}{26-09-2018}{Peter Gorm Larsen}{Added material from Fortiss.}

%
%
\begin{document}
\maketitle
%
%
%
%%%% Document abstract page %%%% 
\section*{Abstract}
\label{sec:abstract}
%
This user manual for the INTO-CPS tool chain, an update of Deliverable D4.3a \cite{INTOCPSD4.3a} that was developed inside the INTO-CPS H2020 project and it is now taken further inside the INTO-CPS association.
%
It is targeted at those wishing to make use of the INTO-CPS technology to design and validate cyber-physical systems.
%
This user manual is concerned with those aspects of the tool chain relevant to end-users, so it is necessarily high-level.
%
Other deliverables from the INTO-CPS project discuss finer details of individual components, including theoretical foundations (Deliverables D4.3b \cite{INTOCPSD4.3b}, D4.2c \cite{INTOCPSD4.2c}, D4.3c \cite{INTOCPSD4.3c}, D2.3a \cite{INTOCPSD2.3a}, D2.2b \cite{INTOCPSD2.2b}, D2.3b \cite{INTOCPSD2.3b}, D2.3c \cite{INTOCPSD2.3c}), methods and guidelines (Deliverables D3.3a \cite{INTOCPSD3.3a} and D3.6 \cite{INTOCPSD3.6}) and software design decisions (Deliverables D4.3d \cite{INTOCPSD4.3d}, D5.2a \cite{INTOCPSD5.2a}, D5.3c \cite{INTOCPSD5.3c}, D5.3d \cite{INTOCPSD5.3d}, D5.3e \cite{INTOCPSD5.3e}).
%
\newpage
%
%%%% Document table of contents page %%%% 
\tableofcontents
\newpage
%
%
%
%%%% Document Content %%%% 
%% \chapter{Chapter Title} %% if intocpslargereport is in use
%\begin{assumption}
%
%
%
\input{sections/intro.tex}
\clearpage
\input{sections/intocpsoverview.tex}
\clearpage
\input{sections/intoapp.tex}
\clearpage
\input{sections/modelioandsysml.tex}
\clearpage
\input{sections/separatetools.tex}
\clearpage
\input{sections/dse.tex}
\clearpage % Force insertion of floating environments
\input{sections/rttester.tex}
\clearpage
\input{sections/traceability.tex}
\clearpage % Force insertion of floating environments\input{sections/codegen.tex}
\input{sections/codegen.tex}
\clearpage
\input{sections/issue-handling.tex}
\clearpage
\input{sections/conclusions.tex}
\clearpage
%
%
%
%
%%%% Bibliography %%%%
\bibliographystyle{alpha}
\bibliography{bibliography} 
\label{ch:bib} %label to refer to
%
%
%
\clearpage
%
%
%
\appendix
\input{appendices/acronyms.tex}
\clearpage
\input{appendices/backgroundontools.tex}
\clearpage
\input{appendices/principles.tex}
%
%
%
\end{document}
